
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{geometry}
\usepackage[ampersand]{easylist}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Pavanan M S}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
% \def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Resume},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.75\linewidth}
  Thiruvonam, Ram Nagar, Vadakkanthara (PO), Palakkad - 678012 \\
  Phone: 9497352789 \\
  Email: pavananms@gmail.com\\
  D.O.B: 03 - 11 - 1993 \\

\end{minipage}

\hline
\section*{Education}

\begin{tabular}{p{5cm} p{4cm} l}
  Bachelor of Technology, Computer Science and engineering & Govt Engineering College, Palakkad (2011-2015) &
  CGPA - 6.3 (First class) \\ \\
  Kerala Higher secondary, Computer Science & PMGHSS, Palakkad & Percentage - 89.5\% \\ \\
  SSLC - Kerala & BEMHSS, Palakkad & Grade - Full A+ ( above 90\% )

\end{tabular}

\hline
\section*{Work History}
\begin{itemize}
\item {\bf THINKBRIDGE}
\item Software Engineer, Pune, March 2019 -  July 2020
\end{itemize}
\begin{itemize}
\item {\bf OPTION-3 CONSULTANCY}
\item Jiffy Implementation, Bangalore, february 2017 - December 2018
\end{itemize}
\subsection*{Contributions}
\begin{easylist}[itemize]

  & Worked In Jiffy Data Interface, a python django project used as a data interface for RPA projects.
  & Worked in Robotic Process Automation using Jiffy.
  & Worked as part of the implemetation team to understand business requirements and design automation flows for businesses.
\vspace{0.1in}
\end{easylist}
\hline
\begin{itemize}
\item {\bf MAKE ME FREE}

\item Software engineer, Bangalore, January 2016 - December 2016
\end{itemize}

\subsection*{Contributions}
\begin{easylist}[itemize]
  & Created REST API's in background application to serve front end requests.
  & worked on webpack, reactjs apps
  & Streamlined deployment process by developing continuous integration tools.
  & Implemented Authentication to process user tokens in backend application.
  & Created automated test scripts for testing websites.
  & Created automated deployment script to setup production and development environment.

\end{easylist}
\vspace{0.1in}
\newpage
\section*{Skills}

\begin{easylist}[itemize]
& Python, Django

& Erlang Devolopment

& web devolopment: Erlang-Cowboy, Django, Html5, Javascript(nodejs, reactjs), Webpack, Python

& Version control: Git

& Database: Postgresql, Redis, Mnesia

& Continuos Integration: Jenkins CI

& Automation scripts: Ansible

& Functional web testing: Jmeter, Selenium

& Monitoring tools: Graphite, Grafana, Icinga

& Documentation: Swagger-UI

& Cloud : Google cloud, Oauth  
\end{easylist}

\section*{Academic Projects}
\begin{tabular}{l  l}
 { \bf 3D Function Plotter}: & A web application which plots a 3 dimensional\\
		     & interactive graph of a given function.\\
                     &                                                                                     \\
 {\bf Virtual Tryouts Using Augmented Reality}: & A Web application which lets \\
					 & a user tryout wearables like watch,specs etc. \\

\end{tabular}
\vspace{0.1in}
\hline

\section*{Other Activities}
\begin{easylist}[itemize]
& Actively participated and coordinated activities in FOSS cell GEC Sreekrishnapuram.
& Represented Kerala Team in National school chess.
\end{easylist}
\vspace{0.1in}
\hline

%\section*{Web Presence}
%\begin{easylist}[itemize]
% & https://pavananms.wordpress.com/
% & https://github.com/pavananms
%\end{easylist}



\end{document}
